Convex Surrogates via Polyhedral Losses

### 2019-02-01 cvx-fin.tex
Some dimension reduction in my note, and started the list of papers for lit review before dinner

>>>>

\subsection{Related works}
A brief history of the convex surrogate.
\jessie{Will do once there is food in my stomach... should be ready by the morning.}
\begin{itemize}
	\item On the Algorithmic Implementation of Multiclass Kernel-based Vector Machines (Crammer and Singer 2001?)
	\item \cite{bartlett2006convexity}
	\item Classification with a Reject Option using Hinge Loss (Bartlett Wegkamp 2008)
	\item \cite{ramaswamy2018consistent} (Originally in 2014... new version in 2018.)
	\item \cite{agarwal2015consistent}
	\item \cite{ramaswamy2016convex}
\end{itemize}

### 2019-02-01 jessie-writeup/n9-not-3-embed.tex
Some dimension reduction in my note, and started the list of papers for lit review before dinner

@@

>>>>

\newcommand{\simplex}{\Delta_{\Y}}

@@

\newpage
\begin{lemma}
	Consider $\Gamma:\simplex \toto \reals^2$ embedding a finite property $\gamma: \simplex \toto \R$, and $S := \{u \in \reals^2 : \Gamma_u \neq \emptyset\}$.

	If $\Gamma$ is $2$-embeddable, then there for any line $l \in \reals^2$, the property $\Gamma|_{S\cap l}$ is $1$-embeddable.
\end{lemma}

\jessie{Does this not work for 6 as well?}
\begin{theorem}
	The abstain($\alpha$) property with $\alpha > 1/2$ and $|\Y| = 6$ is not $2$-embeddable.
\end{theorem}
\begin{proof}
  We use the fact that abstain($\alpha > 1/2$)  with $|\Y| = 3$ is not $1$-embeddable.
  Additionally, for any embedding $\R'$, there is line $\l$ such that $\Gamma|_{S \cap l}$ is reduced to abstain($\alpha > 1/2$)  with $|\Y| = 3$.

  Let $\Gamma:\simplex \toto \R'$ embed the finite property $\gamma$, which is the 
  For each outcome $i \neq a$, we know $\conv(\{i,a\}) \subseteq S$.
	In fact, $S = \cup_{i \in \R'} \conv(\{i,a\})$.

  The set $S$ is then a ``star'' in $\reals^2$.
  (Note that if $a$ is not embedded in the convex hull of the reports, then there is a line $l$ that intersects $\conv(\{i,a\}$ for all reports $i$.)

  Since each report $i$ must be embedded at least $\epsilon$ far away from $a$, consider $\theta_{i,j}$ to be the angle between embedded reports $i$ and $j$, treating $a$ as the origin, without loss of generality.

  Since $\sum_{i=1}^6 \theta_{i,i+2} =720$, there must be some angles $\theta_{i,i+1} + \theta_{i+1,i+2} = \theta_{i,i+2} \leq 120^o < 180^o$.
  The line $l$ can then intersect $\conv(\{i,a\})$, $\conv(\{i+1, a\})$, and $\conv(\{i+2, a\})$ as it can be thought of as having an angle of $180^o$.

  Therefore, for any $2$-embedding of abstain($\alpha > 1/2$) with $n \geq 6$, there is a reduction to a $1$-embedding of abstain($\alpha > 1/2$) for $n = 3$.
  Since this above is not $1$-embeddable, we conclude that abstain($\alpha > 1/2$) with $n \geq 6$ is not $2$-embeddable.
\end{proof}
